### 2025-11-13 Paper/paperdraft_fall2025.tex
Updates from Overleaf

    I construct novel information on individual hospital executives by scraping publicly available tax forms, and merge this to publicly available data sets containing other hospital characteristics: the American Hospital Association Survey (AHA), the Centers for Medicare and Medicaid Services (CMS) Hospital Compare data and Case Mix Index files, and Healthcare Cost Report Information System (HCRIS) data. Ultimately, I employ this hospital-level data spanning from 2010-2014, which contains executive team characteristics, mortality and readmission rates as measures of quality, and other characteristics. In this section, I describe the institutional setting and data collection process. I include more details on the data construction in \ref{appendixdata}.

@@

    Nonprofit hospitals, as with most nonprofits, are typically governed by a board of directors, whose role is complex, but generally is to set broad goals and provide oversight \cite{council_board_roles_2025}. The board selects executives, the highest level of management of a firm, to carry out day-to-day operations. An executive team usually consists of at least a Chief Executive Officer (CEO) and Chief Financial Officer (CFO), but there is variation in how firms organize executive teams. Some hospital executives specialize in health care settings by earning a degree in health care management, or an MBA specific to health care. There are executive positions that are often filled by someone with clinical training, such as a Chief Medical Officer (CMO), but medical doctors can also fill other executive positions. While some doctors earn additional degrees before stepping into an executive role, this is not a necessary condition to becoming a physician executive.

    Hospital executive teams are understudied partly due to the inaccessibility of granular data. I construct a novel data set of nonprofit hospitals in the US which contains names, titles, and positions of all board members and executives tied to the hospital from 2009-2015. I gather this data from publicly available Tax Form 990s, which every sufficiently large nonprofit files each year in the US. To my knowledge, this is the first large scale gathering of executive names from these forms.\footnote{\citeauthor{brickley2010board} (\citeyear{brickley2010board}) collects compensation data for a select number of hospitals.} All tax-exempt organizations in the US are required to file a Form 990 with Internal Revenue Services (IRS) each year. There are different types of forms, but any organization grossing over \$200,000 must file the most extensive Form 990. Sections of this form include a statement of revenue, statement of functional expenses, a balance sheet, and, as used in this project, a list of all key employees, executives, and board members.

    For each hospital in the tax form data, I merge to hospital matches in the AHA data based on name and location.\footnote{I assess the observable differences between matched and non-matched hospitals in Appendix \ref{app:matched}, and conclude that the samples are overall similar apart from an under-sampling of hospitals that belong to systems.} For all hospitals that can be matched to a general hospital in the AHA data, I use optical character recognition (OCR) methods to extract the names, titles, and positions of each listed executive from its Tax Form 990. While board members are an important aspect of hospital organization, I do not include them in this analysis as they are beyond the scope of this paper. I extract text spanning 2009-2015, but I retain a much larger sample of hospitals by limiting to hospitals that have text information in 2010-2014. This yields 847 nonprofit hospitals that are (1) matched to AHA data, and (2) contain complete leadership information in each year from 2010-2014. For clarity, I include a table outlining the number of observations in each sample limitation in Table \ref{tab:sample}.

    \begin{table}[ht!]
    \centering
    \caption{\label{tab:sample}Observations in Sample Limitations}
    \centering
    \begin{tabular}[t]{lc}
    \toprule
    Sample & Num. Observations\\
    \toprule
    Hospital EINs & 5,588\\
    \addlinespace
    Hospital EINs Matched to AHA Hospital or System \hspace{2mm} & 1,340\\
    \addlinespace
    Hospital EINs Match to AHA Hospital Only & 1,152\\
    \addlinespace
    Hospitals with Leadership Info Years 2010-2014 & 847\\
    \bottomrule
    \end{tabular}
    \end{table}

    Clinical training need not be limited to physicians. However, those are the most common and verifiable clinicians in the data. For the main analysis, I verify clinical training of those who are identified as doctors, and obtain additional information about clinically trained executives by matching names to the National Plan and Provider Enumeration System (NPPES) database of all registered physicians. I present a table of means for various characteristics of doctor executives in the data in Table \ref{doc_sumstats}. In total, there are 813 clinically trained executives. On average, they are 52 years old, and 11\% of clinically trained executives are female. While it is more likely they are a Chief Medical Officer than a Chief Executive Officer, still less than a third are CMOs. The most common specialty is internal medicine. While I cannot perfectly verify nurse experience in the data, in Appendix \ref{app:nurses}, I include executives who are marked as registered nurses in the tax forms. The results are similar to those of the main analysis, which is not surprising given that only 0.5\% of executives have a nursing title.

@@

    As the organization of specific c-suite positions can vary drastically across hospitals, I focus on executive teams as a whole instead of specific positions. It is not uncommon for two hospitals to have the same position but the tasks performed be drastically different, or to have two distinct positions that essentially perform the same tasks. I utilize various hospital-level characterizations based on their executive team, such as the existence of a clinically trained executive, the number of clinically trained executives, the number of total executives, and whether the hospital has a Chief Medical Officer.

@@

    The purpose of this paper is to investigate hospital behavior in the midst of financial incentives that change how hospitals receive payment depending on quality. Two programs were passed as part of the Affordable Care Act that focused on pay-for-performance incentives for hospitals: the Hospital Readmissions Reduction Program (HRRP), and the Hospital Value Based Purchasing Program (HVBP). HRRP focused on penalizing hospitals with poor quality, and HVBP focused on rewarding hospitals with high quality or show improvement in quality.

    In October 2011, the Center for Medicare and Medicaid Services (CMS) released a set of rules under HRRP mandating penalties for hospitals with above average readmission rates. The goal of HRRP is to lower readmissions through better care coordination, less initial stay complications, and better post-care instructions. Beginning in October 2012, hospitals with higher readmission rates than the national average in pneumonia, heart failure, or AMI (after adjusting for demographic characteristics) receive a fixed lower reimbursement rate for all Medicare patients seen in their hospital. Penalties are given in the form of a fixed rate reduction of 1-3\% for every Medicare patient regardless of the condition. Excess readmission rates are calculated using a rolling look-back period of 3 years to determine whether the hospital is penalized. Therefore, hospitals had incentive to react immediately once details of the program were announced in October of 2011.

    I focus on outcomes of readmission and mortality rates, which are publicly available at the hospital-condition level in CMS Hospital Compare. I combine rates for pneumonia, AMI, and heart failure (the relevant HRRP conditions) into a weighted average based on the number of patients in each condition.

@@

    In Table \ref{tab:sumstats_samples_stable}, I present means of relevant variables for several hospital samples used throughout the paper. First, in column (1), are means for hospitals who have a clinical executive at any point in time. Column (2) contains means for hospitals who have a clinical executive for the entire sample period, and column (3) shows means for hospitals who never have a clinical executive in the sample period. The main analysis compares hospitals in columns (2) and (3), and supplemental analyses leverage hospitals in column (1).

@@

    Comparing columns (2) and (3), hospitals that never have a clinical executive are smaller, less likely to be an academic medical center, and less likely to be affiliated with a system. Further, they have smaller executive teams on average by 1-2 people, and are less likely to have anyone acting as a designated CMO. Finally, in regards to exposure to pay-for-performance programs, hospitals who never have clinical executives are less likely to receive benefits from the HVBP Program, but seem more similar to hospitals with clinical leadership in terms of penalties from HRRP.

    Next, I plot weighted average readmission rates, mortality rates, and patient case mix index across time for different hospital types in Figure \ref{fig:outcomes_graph}. The effective start year of pay-for-performance incentives is shown as a dotted line in 2012. Average readmission rates trend similarly prior to 2012, and all hospital types exhibit a decrease in raw readmission rates after 2012. However, there is a faster rate of decrease for hospitals who have a clinically trained executive at some point, or who never have a clinically trained executive. When considering mortality, there is not a drastic change in 2012 for any hospital type, but hospitals who always have a clinical executive continue on an increasing trend in mortality where the other hospitals types remain more flat.

@@

    \section{Effect of Clinically Trained Executives on Response to Financial Incentives on Quality}\label{sec:clinical}

    I test empirically whether having clinically trained executives matters in how hospitals respond to the pay-for-performance policies effective in 2012. The quality metrics targeted by the programs are readmission and mortality rates, so I focus on these measures as outcomes. To first analyze a clear control and treatment group, I limit the sample to hospitals who always have clinical executives or never have clinical executives. That is, the hospitals in this analysis do not change their propensity to hire a clinical executive during the sample period.\footnote{An important assumption for this analysis is that this sample selection is not correlated with the program enactment. I investigate this assumption in Section \ref{sec:changes}, and find no evidence that hospitals are more or less likely to change their propensity to hire a clinical executive because of the pay-for-performance programs.} I employ a two-way-fixed-effects strategy as follows:

@@

    \noindent where the variable $y_{ht}$ is one of the outcome variables capturing readmission or mortality rates discussed in Section \ref{sec:hrrp}, and $\gamma_h$ and $\delta_t$ are hospital and time fixed effects, respectively. The coefficient of interest is $\beta$, capturing the effect of having a clinician on change in quality after 2012, when pay-for-performance policies were rolled out. All hospitals had incentive to improve quality in response to the policy change, as penalties and payments are determined by comparing quality among hospitals. Thus, I leverage the timing of the policy change, rather than the policies themselves.

    One may be concerned about potential differences in quality trends between clinical and non-clinical executive team hospitals leading to a violation in the parallel trends assumption. To account for this, I ultimately implement a synthetic difference-in-differences strategy (\cite{arkhangelsky2021synthetic}), which weights more heavily any non-clinical team hospitals with pre-trends similar to clinical team hospitals in the outcome being considered, essentially guaranteeing no differential pre-trends between always and never clinical teams. Using this strategy, the never-clinical group consists of approximately 240 hospitals, and I show the fairly uniform distribution of their weights in Appendix \ref{app:sumstats}. As a robustness check, I also pre-select the sample of always and never clinical hospitals using the Coarsened Exact Matching (CEM) procedure as described by \citeauthor{azoulay2010superstar} (\citeyear{azoulay2010superstar}). I match based on observable characteristics such as hospital size, number of patients in each condition, and eventual penalty status. For brevity, I only present the synthetic difference-in-differences results here. In Appendix \ref{app:otherestimations}, I show that the results are robust to using standard two-way-fixed-effects, matching, or synthetic control.

    For identification, I assume that under the weighted clinical and non-clinical hospital composition, trends would have continued to be parallel absent the incentive change in 2012. This includes an implicit assumption that no other event occurred in 2012 correlated with both the outcomes and composition of leadership team. Finally, I assume that there is no anticipation of the policy change before 2012. The rules of the policies were announced in October of 2011, so 2012 was the first full year that hospitals could meaningfully respond to the policies.

    The estimated difference in readmission and mortality rates between hospitals with and without clinical executives are shown in Figure \ref{fig:clinicalsynthdid}. Estimate $\beta$ is represented in the difference in slope after 2012 when pay-for-performance incentives began. Panel \ref{fig:read_synth_clinical} shows the estimated difference in readmission rates, and reveals that non-clinical teams decrease readmissions by .3 (standard error .13) more than clinical teams. This is a relatively small magnitude given an average readmission rate of 21. However, \citeauthor{gupta2021impacts} (\citeyear{gupta2021impacts}) finds that hospitals overall decrease readmissions by around 3 percentage points due to the program, so this reveals a meaningful difference in behavior relative to the overall behavior change. Using estimates from \citeauthor{gupta2021impacts} (\citeyear{gupta2021impacts}), a 1 percentage point reduction in readmissions across three penalized conditions corresponds to approximately \$110 million in avoided Medicare reimbursements annually. Our results indicate that hospitals led by non-clinical executive teams achieve an additional 0.3 percentage point reduction in readmissions compared to those led by clinical teams. Under the same assumptions, this differential accounts for roughly \$33 million in annual avoided spending—equivalent to 30\% of the savings associated with a 1 percentage point reduction for these conditions. This back-of-the-envelope calculation reflects the incremental contribution of leadership composition to payer-side savings.

@@

    \subsection{Including Nurses in the Sample}\label{app:nurses}

>>>>

    I compile novel data on individual hospital executives by scraping publicly available tax forms, and merge this with publicly available data sets containing other hospital characteristics: the American Hospital Association Survey (AHA), the Centers for Medicare and Medicaid Services (CMS) Hospital Compare data and Case Mix Index files, and Healthcare Cost Report Information System (HCRIS) data. Ultimately, I employ hospital-level data spanning 2010-2014 containing executive team characteristics and mortality and readmission rates as measures of quality. In this section, I describe the institutional setting and data collection process. I include more details on the data construction in Appendix \ref{appendixdata}.

@@

    Nonprofit hospitals, as with most nonprofits, are typically governed by a board of directors, whose role is complex but generally involves setting broad goals and providing oversight (\cite{council_board_roles_2025}). The board selects executives, the highest level of management, to carry out day-to-day operations. An executive team usually consists of at least a Chief Executive Officer (CEO) and Chief Financial Officer (CFO), but there is variation in how firms organize these teams. Some hospital executives specialize in health care administration by earning a degree in health care management, or an MBA specific to health care. There are executive positions that are often filled by someone with clinical training (ex. Chief Medical Officer), but medical doctors can also fill other executive positions. While some doctors earn additional degrees before stepping into an executive role, this is not a necessary condition for becoming a physician executive.

    Hospital executive teams are understudied in part because of the inaccessibility of granular data. I compile a novel data set of nonprofit hospitals in the US which contains names, titles, and positions of all board members and executives associated with each hospital in 2009-2015. I gather this data from publicly available Tax Form 990s. To my knowledge, this is the first large-scale gathering of executive names from these forms.\footnote{\citeauthor{brickley2010board} (\citeyear{brickley2010board}) collect compensation data for a select number of hospitals.} All tax-exempt organizations in the US are required to file a Form 990 with Internal Revenue Services (IRS) each year. There are different types of forms, but any organization grossing over \$200,000 must file the most extensive Form 990. Sections of this form include a statement of revenue, functional expenses, a balance sheet, and, as used in this project, a list of key employees, executives, and board members.

    For each hospital in the tax forms, I merge with hospital records in the AHA data that match based on name and location.\footnote{I assess the observable differences between matched and non-matched hospitals in Appendix \ref{app:matched}, and conclude that the samples are overall similar apart from an under-sampling of hospitals that belong to systems.} For matched hospitals, I use optical character recognition (OCR) methods to extract the names, titles, and positions of each individual listed in the tax form. While board members are an important aspect of hospital organization, I do not include them in this analysis as they are beyond the scope of this paper. I extract text spanning 2009-2015, but I retain a much larger sample of hospitals by restricting the sample to hospitals with text information in 2010-2014. This yields 847 nonprofit hospitals that are matched to the AHA survey and contain complete leadership information in each year from 2010-2014. For clarity, I include a table outlining the number of observations in each sample restriction in Table \ref{tab:sample}.

    \begin{table}[ht!]
    \centering
    \caption{\label{tab:sample}Observations in Sample Restrictions}
    \centering
    \begin{tabular}[t]{lc}
    \toprule
    Sample & Observations\\
    \toprule
    Hospital EINs & 5,588\\
    \addlinespace
    Hospital EINs Matched to AHA Hospital or System \hspace{2mm} & 1,340\\
    \addlinespace
    Hospital EINs Matched to AHA Hospital Only & 1,152\\
    \addlinespace
    Hospitals with Leadership Info, 2010-2014 & 847\\
    \bottomrule
    \end{tabular}
    \end{table}

    Clinical training need not be limited to physicians. However, physicians are the most common and verifiable clinicians in the data. I verify clinical training for individuals identified as doctors, and obtain additional information about clinically trained executives by matching names to the National Plan and Provider Enumeration System (NPPES) database of all registered physicians. I present a table of means for various characteristics of doctor executives in Table \ref{doc_sumstats}. In total, there are 954 clinically trained executives. On average, they are 52 years old, and 11\% of clinically trained executives are female. While it is more likely they are a Chief Medical Officer than a Chief Executive Officer, less than one-third hold CMO positions. The most common specialty is internal medicine. While I cannot perfectly verify nurse experience in the data, in Appendix \ref{app:nurses}, I include executives who are labeled as registered nurses in the tax forms. The results are similar to those of the main analysis, which is unsurprising given that only 0.5\% of executives have a nursing title.

@@

    As the organization of specific C-suite positions can vary drastically across hospitals, I focus on executive teams as a whole rather than individual positions. It is not uncommon for two hospitals to have the same position but the tasks performed to be drastically different, or to have two distinct positions that essentially perform the same tasks. I use various hospital-level characterizations based on their executive team, such as the existence of a clinically trained executive, the number of clinically trained executives, the number of total executives, and whether the hospital has a Chief Medical Officer.

@@

    The purpose of this paper is to investigate hospital behavior under financial incentives that change how hospital quality affects payment. Two programs under the Affordable Care Act that focused on pay-for-performance incentives for hospitals: the Hospital Readmissions Reduction Program (HRRP) and the Hospital Value-Based Purchasing Program (HVBP). HRRP focused on penalizing hospitals with poor quality, and HVBP focused on rewarding hospitals with higher quality.

    In October 2011, the Centers for Medicare \& Medicaid Services (CMS) released a set of rules under HRRP mandating penalties for hospitals with above-average readmission rates. The goal of HRRP is to lower readmissions through better care coordination, less initial stay complications, and better post-care instructions. Beginning in October 2012, hospitals with higher readmission rates than the national average in pneumonia, heart failure, or acute myocardial infarction (AMI) received a fixed lower reimbursement rate for all Medicare patients seen in their hospital. Penalties are given in the form of a fixed-rate reduction of 1-3\% for every Medicare patient regardless of the condition. Excess readmission rates are calculated using a rolling, 3 year look-back period to determine whether the hospital is penalized. Therefore, hospitals had an incentive to react immediately once details of the program were announced in October of 2011.

    The HVBP Program instead rewards hospitals with high quality or significant improvement in quality. Specifically, CMS reduces Medicare payments by 2\% for all eligible hospitals, collects this sum, and redistributes it among the rewarded hospitals. Several quality and cost measures surrounding safety, efficiency, cost reductions, clinical outcomes, and community engagement are combined to create a single metric for each hospital. Hospitals are then compared to the average and are rewarded for being above average quality or showing improvement (\cite{CMS_2023}).

    I focus on outcomes of readmission and mortality, which are publicly available at the hospital-condition-level in CMS Hospital Compare. I combine rates for pneumonia, AMI, and heart failure (the relevant HRRP conditions), weighted by the number of patients in each condition.

@@

    In Table \ref{tab:sumstats_samples_stable}, I present mean values of relevant variables for several hospital samples used throughout the paper. First, in column (1), are means for hospitals that have a clinical executive at any point in time. Column (2) contains means for hospitals that have a clinical executive for the entire sample period, and column (3) shows means for hospitals that never had a clinical executive in the sample period. The main analysis compares hospitals in columns (2) and (3), and supplemental analyses draw on hospitals in column (1).

@@

    Comparing columns (2) and (3), hospitals that never had a clinical executive are smaller, less likely to be an academic medical center, and less likely to be affiliated with a system. Further, they have smaller executive teams by an average of 1-2 people, and are less likely to have a designated CMO. Finally, with regard to exposure to pay-for-performance programs, hospitals that never had clinical executives are less likely to receive benefits from the HVBP Program, but seem more similar to hospitals with clinical leadership in terms of penalties from HRRP.

    Next, I plot weighted average readmission rates, mortality rates, and patient case mix index across time for different hospital types in Figure \ref{fig:outcomes_graph}. The effective start year of pay-for-performance incentives is indicated as a dotted line in 2012. Average readmission rates follow similar trends prior to 2012, and all hospital types exhibit a decrease in raw readmission rates after 2012. However, there is a faster rate of decrease for hospitals that have a clinically trained executive at some point. When considering mortality, there is not a drastic change in 2012 for any hospital type, but hospitals that always have a clinical executive continue on an increasing trend in mortality while the other hospitals types remain relatively flat.

@@

    \section{Effect of Clinical Leadership on Quality Incentive Response}\label{sec:clinical}

    I test empirically whether having clinically trained executives affects how hospitals respond to the pay-for-performance policies effective in 2012. The quality metrics targeted by the programs are readmission and mortality rates, and therefore I focus on these measures as outcomes. To establish a clear control and treatment group, I limit the sample to hospitals that always have clinical executives or never have clinical executives. That is, the hospitals in this analysis do not change their propensity to hire a clinical executive during the sample period.\footnote{An important assumption underlying this analysis is that sample selection is not correlated with the program enactment. I investigate this assumption in Section \ref{sec:changes}, and find no evidence that hospitals are more or less likely to change their propensity to hire a clinical executive because of the pay-for-performance programs.} I employ a two-way fixed effects strategy as follows:

@@

    \noindent where the variable $y_{ht}$ denotes outcome variables (readmission or mortality rates) discussed in Section \ref{sec:hrrp}, and $\gamma_h$ and $\delta_t$ are hospital and time fixed effects, respectively. The coefficient of interest is $\beta$, capturing the effect of having a clinician on changes in quality after 2012, following the implementation of pay-for-performance policies. All hospitals had an incentive to improve quality in response to the policy change, as penalties and payments are determined by comparing quality among hospitals. Thus, I exploit the timing of the policy change rather than variation in policy design.

    One may be concerned about potential differences in quality trends between clinical and non-clinical executive team hospitals leading to a violation in the parallel trends assumption. To account for this, I ultimately implement a synthetic difference-in-differences strategy (\cite{arkhangelsky2021synthetic}), which assigns greater weight to non-clinical team hospitals with pre-trends similar to clinical team hospitals in the outcome being considered, effectively ensuring no differential pre-trends between always and never clinical teams. Using this strategy, the never-clinical group consists of approximately 240 hospitals, and I show the relatively uniform distribution of their weights in Appendix \ref{app:sumstats}. As a robustness check, I also pre-select the sample of always and never clinical hospitals using the Coarsened Exact Matching (CEM) procedure as described by \citeauthor{azoulay2010superstar} (\citeyear{azoulay2010superstar}). I match based on observable characteristics such as hospital size, number of patients in each condition, and eventual penalty status. For brevity, I only present the synthetic difference-in-differences results here. In Appendix \ref{app:otherestimations}, I show that the results are robust to using standard two-way fixed effects, matching, and synthetic control.

    For identification, I assume that given the weighted clinical and non-clinical hospital composition, trends would have continued in a parallel manner in the absence of the incentive change in 2012. This includes an implicit assumption that no other event occurred in 2012 correlated with both the outcomes and composition of the leadership team. Finally, I assume that there is no anticipation of the policy change prior to 2012. The rules of the policies were announced in October 2011, so 2012 was the first full year that hospitals could meaningfully respond to the policies.

    The estimated difference in readmission and mortality rates between hospitals with and without clinical executives is shown in Figure \ref{fig:clinicalsynthdid}. Estimate $\beta$ is represented by the difference in slope after pay-for-performance incentives began. Panel \ref{fig:read_synth_clinical} shows the estimated difference in readmission rates, and reveals that non-clinical teams decrease readmissions by 0.3 (standard error 0.13) more than clinical teams. This is a relatively small magnitude given an average readmission rate of 21\%. However, \citeauthor{gupta2021impacts} (\citeyear{gupta2021impacts}) finds that hospitals overall decrease readmissions by around 3 percentage points due to the program, so this reveals a meaningful difference in behavior relative to the overall behavior change. Using estimates from \citeauthor{gupta2021impacts} (\citeyear{gupta2021impacts}), a 1 percentage point reduction in readmissions across three penalized conditions corresponds to approximately \$110 million in avoided Medicare reimbursements annually. Our results indicate that hospitals led by non-clinical executive teams achieve an additional 0.3 percentage point reduction in readmissions compared to those led by clinical teams. Under the same assumptions, this differential accounts for approximately \$33 million in annual avoided spending—equivalent to 30\% of the savings associated with a 1 percentage point reduction for these conditions. This back-of-the-envelope calculation reflects the incremental contribution of leadership composition to payer-side savings.

@@

    \subsection{Including Nurses as Clinical Executives}\label{app:nurses}

    Everything in this section is identical to the main analysis, apart from the definition of clinical executive. Here, I include executives labeled as a registered nurse in the tax forms as a clinical executives. These are relatively rare, as only of executives say they are a registered nurse. Unlike doctors, there is no publicly available database of all nurses, so the cost of verifying this type of clinical training is much higher. Therefore, in the main body of the paper I only consider doctor executives. However, the results when including nurses are identical, as I show in Figure \ref{fig:nurse_results}.

    \begin{figure}[ht!]
     \caption{\label{fig:nurse_results}Effect of Clinical Training on Readmission/Mortality Rates, Including Nurses}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{Readmission Rates}
         \includegraphics[width=\textwidth]{Objects/nurses_read_md_nomd_synth_graph.pdf}

     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{Mortality Rates}
         \includegraphics[width=\textwidth]{Objects/nurses_mort_md_nomd_synth_graph.pdf}

     \end{subfigure}
     \end{figure}
